Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

A forward model takes as input the aerosol distribution, and outputs
images as if captured at various viewpoints.  In a
\emph{single-scattering} model, any SR changes direction only once on
the way to the camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply.  Under
single-scattering approximation, radiative transfer has three steps
(\cref{fig:groundgrid}):
\begin{inparaenum}[\hfill\bfseries a\upshape)]
\item \label{itm:first} Attenuation of a SR propagating from the top
  of the atmosphere (TOA) to voxel $k$.
\item \label{itm:second} Light scattering at voxel $k$, towards a
  camera.
\item \label{itm:third} Light attenuation on the LOS from voxel $k$ to
  the camera.
\end{inparaenum}
Steps \ref{itm:first} and \ref{itm:third} involve the optical depth
along the light path to and from voxel $k$, analyzed in
\cref{sec:optical-depth}.  Step \ref{itm:second} involves the
scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.

@@

An infinitesimal volume contains aerosols. The extinction and
scattering coefficients due to aerosols in this volume are,
respectively
\begin{equation}
  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
  \;\;,\;\;
  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
  \;.
  \label{eq:betaer}
\end{equation}
The infinitesimal volume contain also air molecules. Hence, the
overall extinction and scattering coefficients in this small volume
are, respectively
\begin{equation}
  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
  \;\;,\;\;
  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
  \;.
  \label{eq:betair}
\end{equation}

Any voxel generally contains both air molecules and aerosols. Voxels
are indexed by $k$ or $q$. As approximation, assume that within any
voxel, the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm
  air}(k)\}$ and the aerosol parameters $\{ \sigma^{\rm
  aerosol}(k),\varpi^{\rm aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are
constants, e.g., corresponding to the value at each voxel
center. These parameters may change between voxels.

>>>>

The atmosphere is discretized into a grid of volume elements (voxels).
A forward model takes as input the aerosol distribution over the grid
of voxels, and outputs images as if captured at various viewpoints.
In a \emph{single-scattering} model, any SR changes direction only
once on the way to the camera. This model is valid in atmospheres that
are not very dense: inside fog and clouds this model does not apply.
Under single-scattering approximation, radiative transfer has three
steps (\cref{fig:groundgrid}):
\begin{inparaenum}[\hfill\bfseries a\upshape)]
\item \label{itm:first} Attenuation of a SR propagating from the top
  of the atmosphere (TOA) to voxel $k$.
\item \label{itm:second} Light scattering at voxel $k$, towards a
  camera.
\item \label{itm:third} Light attenuation on the LOS from voxel $k$ to
  the camera.
\end{inparaenum}
Steps \ref{itm:first} and \ref{itm:third} involve the optical depth
along the light path to and from voxel $k$, analyzed in
\cref{sec:optical-depth}.  Step \ref{itm:second} involves the
scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.

@@

Any voxel generally contains both air molecules and aerosols. Voxels
are indexed by $k$ or $q$. We assume that within any voxel, the
molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
corresponding to the value at each voxel center.
